%-------------------------
% Resume in Latex
% Author : Vigneshwara Chinnadurai
% Based off of: https://github.com/VigneshwaraChinnadurai/resume
% Enhanced: March 2026
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.6in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-.6in}
\addtolength{\textheight}{1.2in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Vigneshwara Chinnadurai} \\ \vspace{1pt}
    \small \faPhone\ 986-555-0901 $|$ 
    \href{mailto:rockingstarvic@gmail.com}{\faEnvelope\ \underline{rockingstarvic@gmail.com}} $|$ 
    \href{https://linkedin.com/in/vigneshwarac}{\faLinkedin\ \underline{linkedin.com/in/vigneshwarac}} $|$
    \href{https://github.com/VigneshwaraChinnadurai}{\faGithub\ \underline{github.com/VigneshwaraChinnadurai}}
\end{center}

%----------SUMMARY----------
\section{Professional Summary}
\small{Senior AI Architect \& Data Scientist with \textbf{8+ years} of experience designing enterprise-scale \textbf{Agentic AI, Generative AI}, and Machine Learning solutions. Pioneer in building \textbf{production-grade Autonomous AI Agent systems} using \textbf{AWS AgentCore SDK}, with expertise in \textbf{Hybrid RAG pipelines}, \textbf{LLM-powered self-critique loops}. Delivered \textbf{\$277M+ measurable business impact} across Fortune 500 clients.}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Senior AI Architect (Senior Consultant)}{January 2022 -- Present}
      {Deloitte Consulting USI}{Bangalore, India}
      
      \vspace{12pt}
      \textit{\small\textbf{Disney TVA Schema Intelligence Chatbot} | AWS Bedrock, Claude 3.7 Sonnet, Agent Forge SDK}
      \resumeItemListStart
        \resumeItem{Architected \textbf{production-grade conversational AI chatbot} using \textbf{custom S3VectorsAgentRuntime} extending AWS AgentCore SDK to handle S3 Vectors' unique \texttt{metadata.text} storage pattern that standard SDK couldn't parse.}
        \resumeItem{Implemented \textbf{intelligent token management} with configurable \texttt{max\_rag\_context\_size} trimming that dynamically truncates retrieval chunks to prevent context overflow.}
        \resumeItem{Innovated \textbf{dual-path KB retrieval}: SDK's \texttt{extract\_retrieval\_chunks} for standard \texttt{content.text} + custom fallback for \texttt{metadata.text} with automatic deduplication.}
        \resumeItem{Created \textbf{follow-up query resolution system} with heuristic-based pronoun detection + URN extraction, rewriting vague queries for improved RAG retrieval.}
        \resumeItem{Optimized memory retrieval latency from \textbf{17+ seconds to under 5 seconds} through memory hook optimization and session stashing before RAG augmentation.}
        \resumeItem{Built \textbf{KB write-back pipeline} with deterministic vector keys enabling immediate queryability of agent-generated summaries without sync delays.}
      \resumeItemListEnd

      \vspace{12pt}
      \textit{\small\textbf{Disney ESPN Game Summary Platform} | AWS Nova Premier, Lambda, Real-time Video AI}
      \resumeItemListStart
        \resumeItem{Developed \textbf{GenAI highlight extraction platform} contributing to \textbf{\$231.76M AWS business expansion}. Architected \textbf{7-step serverless Lambda pipeline}: MediaLive → Kinesis → MediaPackage → S3 → Nova Premier → DynamoDB → Highlights.}
        \resumeItem{Designed \textbf{multimodal prompt engineering} for video analysis with confidence scoring per field, play-type classification, and precise timestamp extraction. Built \texttt{clean\_response\_text()} handling markdown fences and partial JSON.}
        \resumeItem{Expanded architecture from \textbf{NFL} to \textbf{Cricket, Rugby, and Soccer leagues} with ~90\% event capture rate.}
      \resumeItemListEnd

      \vspace{12pt}
      \textit{\small\textbf{HP Enterprise - CXO Talk to Data Platform} | Databricks Genie, Azure OpenAI GPT-4o-mini}
      \resumeItemListStart
        \resumeItem{Built \textbf{AI-powered conversational analytics platform} replacing traditional BI dashboards for executive decision-making. First implementation of \textbf{Databricks Genie's NL-to-SQL} capabilities with user token forwarding.}
        \resumeItem{Architected \textbf{multi-table semantic layer} (2 Fact + 11 Dimension tables) with YAML-based semantic definitions. Implemented \textbf{hallucination reduction} through output validation against schema definitions.}
      \resumeItemListEnd

      \vspace{12pt}
      \textit{\small\textbf{Toyota Demand Forecasting Engine} | LSTM, N-BEATS, Prophet, PySpark}
      \resumeItemListStart
        \resumeItem{Engineered enterprise-scale forecasting system managing \textbf{1.2 million SKU combinations} across 15 distribution centers, reducing annual inventory costs by \textbf{\$46.1 Million} with 70\% WMAPE.}
        \resumeItem{Implemented \textbf{hybrid LSTM architecture} with dual-layer Lambda expansions, \textbf{zero-entry "+1 trick"} for MinMax scaling, and \textbf{ensemble model selection} (LSTM/N-BEATS/SVR/Prophet) per SKU characteristics.}
        \resumeItem{Designed \texttt{orchestrator.py} with \textbf{multiprocessing pool} executing parallel forecasts with YAML-driven multi-environment configuration.}
      \resumeItemListEnd

      \vspace{12pt}
      \textit{\small\textbf{Halliburton Financial Predictive Modeling} | N-BEATS, SARIMAX, Deep Learning}
      \resumeItemListStart
        \resumeItem{Developed \textbf{deep learning forecasting solution} for Accounts Payable/Receivable prediction using \textbf{N-BEATS} and \textbf{SARIMAX} ensemble, achieving \textbf{98\% accuracy} in invoice dispute prediction.}
        \resumeItem{Reduced financial forecast \textbf{delivery time by 98\%} through automated pipeline optimization and multi-variate time series modeling capturing both trend and seasonality patterns.}
      \resumeItemListEnd

      \vspace{12pt}
      \textit{\small\textbf{Firm Initiatives: Agentic AI \& MLOps Estimation Frameworks}}
      \resumeItemListStart
        \resumeItem{Created \textbf{industry-first estimation frameworks} for Agentic AI and MLOps project sizing with 24+ iterations, \textbf{adopted across multiple Deloitte practices} for consistent project scoping.}
      \resumeItemListEnd

      \vspace{12pt}
      \vspace{12pt}
    \resumeSubheading
      {Senior Software Engineer (Machine Learning)}{February 2018 -- January 2022}
      {WIPRO Technologies}{Bangalore, India}
      
      \vspace{12pt}
      \textit{\small\textbf{WIPRO Holmes (R\&D)} | LSTM, Reg-exp, Deep Learning}
      \resumeItemListStart
        \resumeItem{Enhanced Contract Review tool using \textbf{Bi-LSTM + CRF architecture} for sequence labeling of legal clauses in MSAs and SOWs. The \textbf{bidirectional LSTM} captured long-range contextual dependencies while the \textbf{CRF layer} learned valid BIO tag transitions (B-CLAUSE → I-CLAUSE), preventing invalid sequence predictions. Combined with \textbf{character-level embeddings} for OOV legal terminology and \textbf{domain-specific regex patterns} for structured entities (dates, parties, amounts), improved extraction accuracy from \textbf{76\% to 93\%}.}
        \resumeItemListEnd

      \vspace{12pt}
      \textit{\small\textbf{Huawei Video (R\&D)} | DIP, Vector DB, Deep Learning}
      \resumeItemListStart
        \resumeItem{Created data model for \textbf{real-time recommendation pipelines} using \textbf{Deep Interest Network (DIN)} for user behavior modeling. Built \textbf{attention-weighted embeddings} capturing user-item interactions, stored in \textbf{Redis} for low-latency serving + \textbf{Milvus} for vector similarity retrieval. Integrated with \textbf{RASE (Huawei Recommendation-as-a-Service)} for 3 pipelines: \textbf{Hot Broadcast} (trending long-form), \textbf{You May Like} (personalized long-form), and \textbf{Waterfall E2} (short-video infinite scroll).}
        \resumeItemListEnd
        
      \vspace{12pt}
      \textit{\small\textbf{Shell Plc} | CNN, Transfer Learning, Machine Learning}
      \resumeItemListStart
        \resumeItem{Built \textbf{CNN with VGG19 Transfer Learning} in Keras to detect small symbols (valves, pumps, instruments) in P\&ID drawings. Implemented \textbf{Hough Circle Transform} + \textbf{TensorFlow Object Detection API} for geometric shape recognition, automating 2D-to-3D schematic conversion.}
        \resumeItem{Developed \textbf{OCR pipeline} combining \textbf{Tesseract} (for structured text) + \textbf{AWS Textract} (for tables/forms) with custom image preprocessing (contrast enhancement, adaptive thresholding, noise reduction) for legacy engineering document digitization.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Personal R\&D Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Autonomous Multi-Agent Strategic Analysis Engine} $|$ \emph{Gemini 2.5 Flash, Hybrid RAG, Self-Refinement}}{}
          \vspace{12pt}
          \resumeItemListStart
            \resumeItem{\textbf{Genuinely Agentic Architecture}: LLM-powered planning where \texttt{AnalystAgent} autonomously decomposes complex prompts into executable multi-step plans without predefined workflows.}
            \resumeItem{\textbf{Hybrid Retrieval Pipeline}: Custom BM25 sparse + Gemini dense embeddings with \textbf{Reciprocal Rank Fusion (RRF)} + \textbf{LLM-powered reranking} (0-1 relevance scoring).}
            \resumeItem{\textbf{Self-Critique \& Refinement Loop}: Rubric-based critique (Depth/Evidence/Causality/Actionability) with automatic \texttt{NEEDS\_REFINEMENT} detection triggering re-retrieval cycles.}
            \resumeItem{\textbf{Dynamic Tool Generation}: Runtime code synthesis creating callable Python functions from LLM output. \textbf{Graph Memory} with semantic triple extraction for persistent knowledge.}
            \resumeItem{\textbf{Real data integration}: SEC EDGAR XBRL, Google News RSS, Gemini Search Grounding. \textbf{Cost Guard System} with budget caps and aggressive caching.}
          \resumeItemListEnd

      \vspace{12pt}
      \resumeProjectHeading
      \vspace{12pt}
          {\textbf{Quantum Portfolio Optimization Engine} \(MBA Project
          \vspace{12pt}\) $|$ \emph{D-Wave Quantum Annealing, QUBO, Simulated Annealing}}{}
          \resumeItemListStart
            \resumeItem{\textbf{QUBO Formulation from First Principles}: Quadratic Unconstrained Binary Optimization with risk terms (covariance), return rewards (mean returns), and cardinality constraints via penalty functions.}
            \resumeItem{\textbf{Classical-Quantum Benchmark}: Side-by-side scipy max-Sharpe vs. quantum annealing with hyperparameter sweep over \emph{risk \& return}, penalty coefficients.}
            \resumeItem{\textbf{D-Wave Leap QPU Integration}: Production-ready execution with \texttt{EmbeddingComposite} for automatic qubit mapping. Efficient frontier visualization.}
          \resumeItemListEnd

      \vspace{12pt}
      \resumeProjectHeading
      \vspace{12pt}
          {\textbf{LeetCode AI Companion (Android) (Personal Development)} $|$ \emph{Kotlin, Jetpack Compose, Gemini API, GraphQL}}{}
          \resumeItemListStart
            \resumeItem{\textbf{Jetpack Compose UI} with Material Design 3. LeetCode GraphQL integration for daily challenges. \textbf{Gemini generation pipeline} with retry logic.}
            \resumeItem{\textbf{GitHub Push Automation}: One-tap export of solutions to repository. Calendar event integration for completion tracking. Mermaid flow viewer with gestures.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
  \vspace{8pt}
    \resumeSubheading
      {Manipal University}{Jaipur, India}
      {Master of Business Administration, Analytics and Data Science}{August 2024 -- June 2026}
    \resumeSubheading
      {Anna University}{Chennai, India}
      {Bachelor of Engineering, Electrical \& Electronics}{August 2014 -- May 2017}
  \resumeSubHeadingListEnd


%-----------CERTIFICATIONS-----------
\section{Certifications}
\vspace{8pt}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{AWS Certified Machine Learning -- Specialty} $|$ Amazon Web Services (Oct 2021) \\
     \textbf{Delivery Accreditation - AI Agents} $|$ ServiceNow \\
     \textbf{Configure AI Applications to Optimize Search Results} $|$ Google \\
     \textbf{Deep Learning Specialization} $|$ Coursera/Udacity
    }}
 \end{itemize}


%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Agentic AI \& RAG}{: Agent Forge SDK (AWS AgentCore), Strands Agents, Multi-Agent Orchestration, LLM Planning \& Critique, Self-Refinement Loops, Hybrid Retrieval (BM25 + Dense + RRF), LLM Reranking, S3 Vectors, Token-aware Trimming} \\
     \textbf{LLMs \& Foundation Models}{: Claude 3.7 Sonnet, GPT-4/4o-mini, AWS Nova Premier, Gemini 2.5 Flash, Llama 3, Amazon Titan Embed v2} \\
     \textbf{Quantum Computing}{: D-Wave Quantum Annealing, QUBO Formulation, Simulated Annealing, D-Wave Leap, Binary Quadratic Models} \\
     \textbf{Deep Learning}{: Transformers (BERT, DiT), CNN (VGG19, ResNet), LSTM, Bi-LSTM, Deep Interest Network (DIN), N-BEATS, Prophet} \\
     \textbf{Cloud \& MLOps}{: AWS (Bedrock, SageMaker, Lambda, S3, MediaLive, Kinesis, SQS, Identity Manager, Media Package, Media Convert), Azure (OpenAI), GCP (Vertex AI), Docker, Kubernetes, Airflow, DataBricks} \\
     \textbf{Languages \& Data}{: Python, PySpark, SQL, Kotlin (Android), Pandas, NumPy, TensorFlow, PyTorch}
    }}
 \end{itemize}


%-----------KEY ACHIEVEMENTS-----------
\section{Key Achievements}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{\$46.1M} annual inventory savings at Toyota $|$ 
     \textbf{\$231.76M} AWS expansion via Disney ESPN $|$ 
     \textbf{30\%} latency reduction (70s→50s) $|$ 
     \textbf{93\%} contract extraction accuracy $|$ 
     \textbf{1.2M SKUs} forecasting scale $|$ 
     \textbf{4+ Fortune 500} production deployments
    }}
 \end{itemize}


%-------------------------------------------
\end{document}



%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Vigneshwara Chinnadurai} \\ \vspace{1pt}
    \small 986-555-0901 $|$ \href{mailto:x@x.com}{\underline{rockingstarvic@gmail.com}} $|$ 
    \href{https://linkedin.com/in/...}{\underline{linkedin.com/in/vigneshwarac}} $|$
    \href{https://github.com/...}{\underline{github.com/VigneshwaraChinnadurai}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Manipal University}{Jaipur, India}
      {Master of Business Administration, Analytics and Data Science}{August 2024 -- June 2026}
    \resumeSubheading
      {Anna University - Chennai}{Tamilnadu, India}
      {Bachelor's in Electrical Engineering}{August 2014 -- May 2017}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Senior Machine Learning Engineer (Senior Consultant)}{January 2022 -- Present}
      {Deloitte Consulting USI}{Bangalore, India}
      \resumeItemListStart
        \resumeItem{Developed a forecasting engine for a major automotive manufacturer, managing 1.2 million SKU combinations across fifteen distribution centers. Utilized LSTM and Prophet, achieving 70\% WMAPE and reducing annual inventory holding costs by \$46.1 Million.}
        \resumeItem{Developed a deep learning solution to forecast Accounts Payable/Receivable. Reduced invoice dispute prediction errors, achieving 98\% accuracy and cutting delivery time by 98\%.}
        \resumeItem{Engineered an automated highlight generation platform for the sports media industry using a serverless AWS architecture with Amazon Bedrock. The platform processes multiple live video streams in real-time, using AI/ML to detect key events such as 15+ yard passes, all scoring plays, and turnovers with a ~90\% capture rate, which is expected to exceed 98\% with fine-tuning.}
        \resumeItem{Architect-ed a unified, multi-agent AI platform on AWS Bedrock, supporting both conversational and analytical agents from a common, scalable infrastructure. This platform powers an S3-backed RAG chat bot for enterprise knowledge discovery and a specialized agent that automates the analysis of JSON schema changes by enriching data with JIRA and GitHub context to produce structured, audible summaries.}
        \resumeItem{Orchestrated the development and implementation of a Databricks Genie-powered solution, streamlining and automating CCO funnel data analytics. This initiative provided enhanced visibility into the customer conversion pipeline, enabling data-driven decision-making and optimization of the sales process.}        
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    % \resumeSubheading
    %   {Information Technology Support Specialist}{Sep. 2018 -- Present}
    %   {Southwestern University}{Georgetown, TX}
    %   \resumeItemListStart
    %     \resumeItem{Communicate with managers to set up campus computers used on campus}
    %     \resumeItem{Assess and troubleshoot computer problems brought by students, faculty and staff}
    %     \resumeItem{Maintain upkeep of computers, classroom equipment, and 200 printers across campus}
    % \resumeItemListEnd

    \resumeSubheading
      {Senior Software Engineer (Machine Learning)}{February 2018 -- January 2022}
      {WIPRO Technologies (WIPRO Holmes Team)}{Bangalore, India}
      \resumeItemListStart
        \resumeItem{Enhanced a Contract Review tool using Bi-LSTM and CRF to extract clauses from MSAs and SOWs. Improved extraction accuracy from 76\% to 93\% through hyperparameter tuning and Regex pattern matching.}
        \resumeItem{Developed a CNN (VGG19) model with Transfer Learning to detect symbols and objects within AutoCAD drawings for an Oil \& Gas client, automating the conversion of 2D schematics into 3D projections.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Personal Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Detect Emotions of Your Favorite Cartoon (HackerEarth)} $|$ \emph{Python, ML}}{June 2020 -- Present}
          \resumeItemListStart
            \resumeItem{\textbf{Objective:} To build a model that detects emotions in cartoon characters by extracting image frames from a given video clip to use as a dataset.}
            \resumeItem{\textbf{Key Challenges:} The project involved working with a very small and imbalanced dataset, which required special techniques to ensure model performance.}
            \resumeItem{\textbf{Achievement:} Secured an honorable ranking in the competition by achieving 73\% accuracy with the model.}
          \resumeItemListEnd
      % \resumeProjectHeading
      %     {\textbf{Simple Paintball} $|$ \emph{Spigot API, Java, Maven, TravisCI, Git}}{May 2018 -- May 2020}
      %     \resumeItemListStart
      %       \resumeItem{Developed a Minecraft server plugin to entertain kids during free time for a previous job}
      %       \resumeItem{Published plugin to websites gaining 2K+ downloads and an average 4.5/5-star review}
      %       \resumeItem{Implemented continuous delivery using TravisCI to build the plugin upon new a release}
      %       \resumeItem{Collaborated with Minecraft server administrators to suggest features and get feedback about the plugin}
      %     \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    \textbf{Languages}{: Python, SQL (Postgres)} \\
     \textbf{Frameworks}{: LangGraph, TensorFlow, CUDA, Keras, SK-Learn} \\
     \textbf{Developer Tools}{: Git, AWS (SageMaker, Bedrock), DataBricks, Google Cloud Platform (Vertex AI), VS Code} \\
     \textbf{Libraries \& Models}{: LLMs (GPT, Llama), Transformers (BERT, DiT), CNNs, Prophet, Spacy, Pandas, NumPy, Matplotlib}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
